Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives

### 2015-01-27 paper/Diversity_MS.tex
Fixed first page issues

%-----------------------------------------
%Current title page 
%NB PeerJ don't want a title page: just the author details but I haven't figured out how to do that without losing the formatting of the rest of the manuscript
%I may need to get rid of the lists of tables and figures at the end: they want titles and legends to be on the same page as the figure/table
%----------------------------------------
\title{Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives}

\author{Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$}
\affiliation{\noindent{\footnotesize
$^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
$^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
$^*$Corresponding author: ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland.\\ Tel: +353 1 896 1926.\\}}
\date{}	% To give blank date

\runninghead{Cranial morphological diversity in tenrecs }

\keywords{geometric morphometrics, golden moles, morphological diversity, tenrecs}
%---------------------------------------------------------------
% Start of document
\begin{document}
\modulolinenumbers[1] 	% Line numbering on every line

\mstitlepage			% Instead of \maketitle you can use the nice template to get it looking like a manuscript
\parindent=1.5em		% Changes paragraph indenting so it's not so big
\addtolength{\parskip}{.3em} % Changes spacing between sections so it's smaller
%****************************************************
%Abstract
%Peer J wants the abstract as a separate document

@@

	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}. However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}. Variation in skull shape is only one aspect of overall morphology. Quantifying variation in other morphological traits could yield different patterns. Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
%**********************************
\section{Conclusions}
	We have presented the first quantitative investigation of morphological diversity in tenrecs. Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the Family. Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required. However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs. 
%*******************************
\section{Acknowledgements} %PeerJ have a separate section for funding acknowledgements
	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments. Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
%********************************
\bibliographystyle{sysbio} 
\bibliography{refs_paper}

>>>>

%-----------------------------------------
%Current title page 
%NB PeerJ don't want a title page: just the author details but I haven't figured out how to do that without losing the formatting of the rest of the manuscript
%I may need to get rid of the lists of tables and figures at the end: they want titles and legends to be on the same page as the figure/table
%----------------------------------------

%---------------------------------------------------------------
% Start of document
\begin{document}
\modulolinenumbers[1] 	% Line numbering on every line

\parindent=1.5em		% Changes paragraph indenting so it's not so big
\addtolength{\parskip}{.3em} % Changes spacing between sections so it's smaller

\noindent
\textsc{Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$}\\

\noindent
$^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
\noindent
$^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
\noindent
$^*$Corresponding author: Natalie Cooper; ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland. Tel: +353 1 896 1926.\\

\newpage
%****************************************************
%Abstract
%Peer J wants the abstract as a separate document

@@

	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}. However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}. Variation in skull shape is only one aspect of overall morphology. Quantifying variation in other morphological traits could yield different patterns. Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
%**********************************
\section{Conclusions}
	We have presented the first quantitative investigation of morphological diversity in tenrecs. Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the Family. Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required. However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs. 
%*******************************
\section{Acknowledgements} %PeerJ have a separate section for funding acknowledgements
	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments. Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute NMNH), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
%********************************
\bibliographystyle{sysbio} 
\bibliography{refs_paper}
